Depth over distance: Hawaiian cryptic reef communities are more distinct across ~90 m depth than ~2500 km of shallow habitat

### 2024-01-05 manuscript.Rmd
a bunch of updates

top_list <- function(species,n,units,len=4,fig=NULL) {
  s1 <- map_chr(species,format_species)
  s2 <- map2_chr(n,units,~{
    if (is.null(fig)) {
      str_glue("({.x} individuals on {.y} units)")
    } else {
      str_glue("({.x} individuals on {.y} units; [@fig:{fig}[]{{{{}}}}{{.y}}])")
    }
  })
  if (!is.null(fig)) {
    s2 <- map2_chr(s2,LETTERS[seq(length(s2))],~str_glue(.x))
  }
  ss <- str_c(s1," ",s2)
  ss[1:(len-1)] %>%
    str_c(collapse=", ") %>%
    str_c(", and ",ss[len])
}

@@

The structure and composition of coral reef communities is influenced by a suite of environmental and anthropogenic factors, yet their nature and makeup remain poorly resolved. Coral reefs are among the most diverse habitats in the world, yet they face increasing threats of degradation, including climate-driven bleaching and phase shifts to alternate ecological regimes [@grahamManagingResilienceReverse2013; @norstromAlternativeStatesCoral2009; @pandolfiGlobalTrajectoriesLongTerm2003]. In the face of these and other threats, understanding drivers of community structure is critically important [@hughesRisingChallengeSustaining2010; @pageSeekingResistanceCoral2019]. To date, the majority of efforts in this area have focused on conspicuous taxa such as corals and fishes [e.g., @benfieldComparisonCoralReef2008; @caballero-aragonWaveExposureTemperature2023; @kaneTrophicDesignationLive2017; @langeWaveExposureShapes2021; @vanlierHabitatConnectivityComplexity2018] or microbes [e.g., @desouzaImportanceDepthTemperature2023; @morrowEnvironmentalDriversMicrobial2016]. However, these taxa make up a minority of coral reef biodiversity and thus may not be indicative of community patterns overall [[cite?]]{.mark}. Here, we investigate the factors influencing the community structure of a group of cryptic coral reef taxa across the Hawaiian Archipelago. <!--Say something about depth here, but I'm not sure what or how-->

@@

A likely important but under-investigated aspect of coral reef community structure is depth. Most studies to date have focused on the upper ~30 m of the water column, yet coral reefs and associated communities are known to extend beyond 150 m [@pyleExploringDeepCoral1996; @pyleMesophoticCoralEcosystems2019], with scleractinian corals reported to 170 m [@rouzeSymbioticAssociationsDeepest2021]. As much as two thirds of coral reef ecosystems lie in this under-explored zone [@hindersteinThemeSectionMesophotic2010]. These habitats, known as mesophotic coral ecosystems (MCEs), are typically defined as those extending from ~30--150 m depth [@hindersteinThemeSectionMesophotic2010; @kahngCommunityEcologyMesophotic2010]. <!--and were believed to experience dampened disturbances in comparison to shallow reefs and could therefore act as deep water refugia for shallow reef species threatened by anthropogenic impacts --> They have been hypothesized as possible refugia from disturbances on shallow reefs [@bongaertsAssessingDeepReef2010; @smithDepthRefugiumCatastrophic2014; @holsteinFertileFathomsDeep2015; @muirSpeciesIdentityDepth2017], although a number of studies have found evidence that deep reefs are unique and uniquely threatened, challenging this notion [@diazLightTemperatureDrive; @diazMesophoticCoralBleaching2023; @hobanPlumbingDepthsEnvironmental2023; @hurleyAssessmentShallowMesophotic2016; @kaneHighLevelsMesophotic2014; @pinheiroDeepReefFishes2019; @rochaMesophoticCoralEcosystems2018]. <!--However, recent literature describing species compositions along depth gradients reveal a more complex picture among taxa and locations because some groups may use mesophotic reefs as a refuge in some places, while others show community turnover with depth such that MCE habitats are ecologically distinct from adjacent shallow water coral reefs [@hurleyAssessmentShallowMesophotic2016; @smithCaribbeanMesophoticCoral2016; @semmlerAreMesophoticCoral2017; @bongaertsDeepReefsAre2017; @rochaMesophoticCoralEcosystems2018]. Further, there are a range of connections depending on the taxa – large, mobile organisms like fish tend to have more shared species across depth than sedentary organisms such as corals and algae, but even among the fishes the community structure of MCEs is often distinct [@kaneHighLevelsMesophotic2014; @pyleComprehensiveInvestigationMesophotic2016 ; @asherMesophoticDepthGradients2017; @fukunagaChangesMesophoticReef2017; @colemanShiftingReefFish2018; @pinheiroDeepReefFishes2019]. Although the majority of coral reef biodiversity consists of the algal and invertebrate cryptobenthic organisms living on and within the reef structure [@fautinOverviewMarineBiodiversity2010; @knowltonCoralReefBiodiversity2010; @fisherSpeciesRichnessCoral2015], the studies listed above focus almost exclusively on the corals and fishes which are more easily surveyed.--> Given the strong reported differences between deep and shallow reefs across taxa and the paucity of research on drivers of cryptic coral reef community variation, we sought to answer the following research questions: (i) How do shallow crab communities vary along the natural and anthropogenic gradients of the Hawaiian Archipelago? (ii) Do shallow crab communities differ between the Main and Northwestern Hawaiian Islands? (iii) What environmental and/or anthropogenic factors drive crab community structure in shallow coral reefs across the Hawaiian Archipelago? (iv) What are the relative contributions of depth (shallow vs. mesophotic) and island region to crab community variation across the Hawaiian Archipelago?

@@

@@

ggplot() +
  geom_sf(data=hawaii %>% st_transform(transformer), color="black", fill="green", linewidth=0.4) +
  geom_sf(data=pmnm,color=NA,fill="#6ed8f6",alpha=0.2) +
  geom_sf(data=crab_sites %>% st_transform(transformer),aes(fill=island),size=3,shape=21,color="black") +
  scale_fill_manual(values=island_pal,name="Island") +
  coord_sf(xlim=box_after[c(1,3)],ylim=box_after[c(2,4)]) +
  scale_x_continuous(breaks = -seq(180, 155, -5)) +
  theme_minimal() +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(legend.text = element_text(size=10),legend.title = element_text(size=12))
cat("{#fig:fig_map}")
```

@@

We used distance-based redundancy analysis (dbRDA; a form of multivariate multiple regression) with `dbrda` to examine the relative contribution of environmental variables to crab community variation across the islands. We first used a stepwise forward selection procedure (`ordiR2step`) to find the variables that best explained community dissimilarity. Then, we sequentially removed variables with the largest variance inflation factors (VIF; calculated using `vif.cca`) until all values were <3, indicating variables were sufficiently uncorrelated. Model significance was assessed using permutation tests with `r num(PERM,1)` permutations in the function `anova`. Continuous variables were scaled to unit variance. We assessed variation among groups using `betadisper` and `adonis2`. These functions implement analysis of multivariate homogeneity of group dispersions (PERMDISP) and multivariate permutational analysis of variance (PERMANOVA) respectively. PERMDISP is used to assess variability within groups and PERMANOVA is used to assess differences among groups. Significance was assessed with permutation tests in both cases. Variation among sampling groups (shallow MHI, shallow NWHI, O&#x02BB;ahu 30 m, 60 m, 90 m) was further examined and visualized using canonical analysis of principal coordinates (CAP) based on discriminant analysis [@andersonCanonicalAnalysisPrincipal2003] as implemented in the `CAPdiscrim` function in `BiodiversityR` [@kindtTreeDiversityAnalysis2005].

@@

Potential environmental drivers of shallow crab community structure were assembled a previous study on environmental drivers of genetic diversity [@selkoeDNACoralReef2016], NOAA's National Coral Reef Monitoring Program (NCRMP), the Pacific Islands Ocean Observing System (PacIOOS), NASA Physical Oceanography Distributed Active Archive Center (PO.DAAC), and NASA Ocean Biology Distributed Active Archive Center (OB.DAAC) ([@tbl:env_table]). For details on how sea-surface temperature and chlorophyll data were compiled and aggregated, see Supplemental material. Due to logistical limitations, environmental data were collected only for shallow samples ($\le$ 30 m).

@@

Environmental variables were strongly clustered according to island group (MHI vs NWHI), with the separation primarily along the direction influenced by human impact, coral cover, sea-surface temperature, and chlorophyll ([@fig:fig_pca]). The best dbRDA model (`r permanova(db_modl,stat="F")`) explained `r pc(RsquareAdj(db_modl)$adj.r.squared,0.01)` (adjusted $\mathrm{R}^2$) of the variability in crab communities across the archipelago ([@fig:fig_dbrda]). `r str_to_sentence(english(nterm))` of the seven environmental variables tested were significant and sufficiently uncorrelated. The two drivers contributing most to explained variation were `r drivers$term[1]` (F = `r num(drivers$stat[1],0.01)`) and `r drivers$term[2]` (F = `r num(drivers$stat[2],0.01)`) ([@tbl:rda_table]).

@@

In the CAP analysis of island group and depth zone, ARMS units were correctly reassigned to groups `r pc(cap_depth$percent/100,0.1)` of the time. The first two axes explained `r pc(cap_var$x,0.1)` and `r pc(cap_var$y,0.1)` of the variation, respectively. Mesophotic samples ($\geq$ 30 m) from O&#x02BB;ahu grouped separately from shallow samples collected across the entire ~2,500 km expanse of the archipelago ([@fig:fig_cap]). Additionally, variability among 30--90 m samples was equivalent to that among all shallow samples, although that was largely due to differences between 30 m and deeper sample groups ([@fig:fig_cap]).

@@

# Discussion {-}
The Hawaiian Archipelago is among the most remote on the planet and encompasses a range of gradients (anthropogenic, biotic, abiotic), making it an ideal area to study the impacts of these factors on species assemblages across space. Human impacts are considerably higher in the populated MHI than in the protected and remote NWHI [@selkoeEvaluatingAnthropogenicThreats2008; @selkoeMapHumanImpacts2009; @selkoeDNACoralReef2016]. Although we did not consider individual effects here, an index representing cumulative anthropogenic impacts was the top driver of brachyuran community structure, similar to previous work examining genetic diversity across the archipelago [@selkoeDNACoralReef2016]. The next-most significant driver, chlorophyll a, can be used as a proxy for primary productivity. Productivity gradients have been reported across the Hawaiian Archipelago, which coincide with differences in coral reef community composition [@selkoeDNACoralReef2016], endemic reef fish dominance [@friedlanderDominanceEndemicsReef2020], and survival rates of top predators [@bakerEffectVariableOceanic2007]. It is not surprising, therefore, that we find differences in the brachyuran crab communities are driven by these same factors across the Hawaiian archipelago.

@@

## Processing of satellite-derived SST and chl-A data
Sea-surface temperature (SST) and chlorophyll A (chl-A) data were retrieved from NASA's Physical Oceanography Distributed Active Archive Center [PO.DAAC; @NASAJPL_2020] and Ocean Biology Distributed Active Archive Center [OB.DAAC; @NASAOceanBiologyProcessingGroup_2022] respectively. Monthly summary datasets were downloaded for 30 randomly subsampled months within each ARMs unit's three-year soaking period, averaged, and values (SST or chl-A) were extracted for the geographic coordinates of each sampling site, with a 300 m surrounding buffer zone.

@@

(p1 + p2) / (p3 + p4) & 
  plot_annotation(tag_levels = "A")
cat("{#fig:fig_alpha}")
```

@@

(p1 + p2) & 
  plot_annotation(tag_levels = "A")
cat("{#fig:fig_alpha2}")
```

@@

>>>>

top_list <- function(species,n,units,len=4,fig=NULL) {
  s1 <- map_chr(species,format_species)
  s2 <- map2_chr(n,units,~{
    if (is.null(fig)) {
      str_glue("({.x} individuals on {.y} units)")
    } else {
      str_glue("({.x} individuals on {.y} units; [@fig:{fig}[]{{{{}}}}{{.y}}])")
    }
  })
  if (!is.null(fig)) {
    s2 <- map2_chr(s2,letters[seq(length(s2))],~str_glue(.x))
  }
  ss <- str_c(s1," ",s2)
  ss[1:(len-1)] %>%
    str_c(collapse=", ") %>%
    str_c(", and ",ss[len])
}

@@

The structure and composition of coral reef communities is influenced by a suite of environmental and anthropogenic factors, yet the nature and makeup of those factors remain poorly resolved. Coral reefs are among the most diverse habitats in the world, and they face increasing threats of degradation, including climate-driven bleaching and phase shifts to alternate ecological regimes [@grahamManagingResilienceReverse2013; @norstromAlternativeStatesCoral2009; @pandolfiGlobalTrajectoriesLongTerm2003], among others. In the face of these and other threats, understanding drivers of community structure is critically important [@hughesRisingChallengeSustaining2010; @pageSeekingResistanceCoral2019]. To date, the majority of efforts in this area have focused on conspicuous taxa such as corals and fishes [e.g., @benfieldComparisonCoralReef2008; @caballero-aragonWaveExposureTemperature2023; @kaneTrophicDesignationLive2017; @langeWaveExposureShapes2021; @vanlierHabitatConnectivityComplexity2018] or microbes [e.g., @desouzaImportanceDepthTemperature2023; @morrowEnvironmentalDriversMicrobial2016]. However, these taxa make up a minority of coral reef biodiversity and thus may not be indicative of community patterns overall [[cite?]]{.mark}. Here, we investigate the factors influencing the community structure of a group of cryptic coral reef taxa across the Hawaiian Archipelago. <!--Say something about depth here, but I'm not sure what or how-->

@@

A likely important but under-investigated aspect of coral reef community structure is depth. Most studies to date have focused on the upper ~30 m of the water column, yet coral reefs and associated communities are known to extend beyond 150 m [@pyleExploringDeepCoral1996; @pyleMesophoticCoralEcosystems2019], with scleractinian corals reported to 170 m [@rouzeSymbioticAssociationsDeepest2021]. As much as two thirds of coral reef ecosystems lie in this under-explored zone [@hindersteinThemeSectionMesophotic2010]. These habitats, known as mesophotic coral ecosystems (MCEs), are typically defined as those extending from ~30--150 m depth [@hindersteinThemeSectionMesophotic2010; @kahngCommunityEcologyMesophotic2010]. <!--and were believed to experience dampened disturbances in comparison to shallow reefs and could therefore act as deep water refugia for shallow reef species threatened by anthropogenic impacts --> They have been hypothesized as possible refugia from disturbances on shallow reefs [@glynnCoralReefBleaching1996; @bongaertsAssessingDeepReef2010; @smithDepthRefugiumCatastrophic2014; @holsteinFertileFathomsDeep2015; @muirSpeciesIdentityDepth2017], although studies have found evidence that deep reefs are unique and uniquely threatened, challenging this notion [@diazLightTemperatureDrive; @diazMesophoticCoralBleaching2023; @hobanPlumbingDepthsEnvironmental2023; @hurleyAssessmentShallowMesophotic2016; @kaneHighLevelsMesophotic2014; @pinheiroDeepReefFishes2019; @rochaMesophoticCoralEcosystems2018]. <!--However, recent literature describing species compositions along depth gradients reveal a more complex picture among taxa and locations because some groups may use mesophotic reefs as a refuge in some places, while others show community turnover with depth such that MCE habitats are ecologically distinct from adjacent shallow water coral reefs [@hurleyAssessmentShallowMesophotic2016; @smithCaribbeanMesophoticCoral2016; @semmlerAreMesophoticCoral2017; @bongaertsDeepReefsAre2017; @rochaMesophoticCoralEcosystems2018]. Further, there are a range of connections depending on the taxa – large, mobile organisms like fish tend to have more shared species across depth than sedentary organisms such as corals and algae, but even among the fishes the community structure of MCEs is often distinct [@kaneHighLevelsMesophotic2014; @pyleComprehensiveInvestigationMesophotic2016 ; @asherMesophoticDepthGradients2017; @fukunagaChangesMesophoticReef2017; @colemanShiftingReefFish2018; @pinheiroDeepReefFishes2019]. Although the majority of coral reef biodiversity consists of the algal and invertebrate cryptobenthic organisms living on and within the reef structure [@fautinOverviewMarineBiodiversity2010; @knowltonCoralReefBiodiversity2010; @fisherSpeciesRichnessCoral2015], the studies listed above focus almost exclusively on the corals and fishes which are more easily surveyed.--> Given the strong reported differences between deep and shallow reefs across taxa and the paucity of research on drivers of cryptic coral reef community variation, we sought to answer the following research questions: (i) How do shallow crab communities vary along the natural and anthropogenic gradients of the Hawaiian Archipelago? (ii) Do shallow crab communities differ between the Main and Northwestern Hawaiian Islands? (iii) What environmental and/or anthropogenic factors drive crab community structure in shallow coral reefs across the Hawaiian Archipelago? (iv) What are the relative contributions of depth (shallow vs. mesophotic) and island region to crab community variation across the Hawaiian Archipelago?

@@

<br><br>

@@

ggplot() +
  geom_sf(data=hawaii %>% st_transform(transformer), color="black", fill="#A3866A", linewidth=0.4) +
  geom_sf(data=pmnm,color=NA,fill="#6ed8f6",alpha=0.2) +
  geom_sf(data=crab_sites %>% st_transform(transformer),aes(fill=island),size=3,shape=21,color="black") +
  scale_fill_manual(values=island_pal,name="Island") +
  coord_sf(xlim=box_after[c(1,3)],ylim=box_after[c(2,4)]) +
  scale_x_continuous(breaks = -seq(180, 155, -5)) +
  theme_minimal() +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(legend.text = element_text(size=10),legend.title = element_text(size=12))
cat("{#fig:fig_map}")
```

<br><br>

@@

We used distance-based redundancy analysis (dbRDA; a form of multivariate multiple regression) with `dbrda` to examine the relative contribution of environmental variables to crab community variation across the islands. We first used a stepwise forward selection procedure (`ordiR2step`) to find the variables that best explained community dissimilarity. Then, we sequentially removed variables with the largest variance inflation factors (VIF; calculated using `vif.cca`) until all values were <3, indicating variables were sufficiently uncorrelated. Model significance was assessed using permutation tests with `r num(PERM,1)` permutations with the function `anova`. All continuous variables were scaled to unit variance.

We assessed variation among groups using `betadisper` and `adonis2`. These functions implement analysis of multivariate homogeneity of group dispersions (PERMDISP) and multivariate permutational analysis of variance (PERMANOVA) respectively. PERMDISP is used to assess variability within groups and PERMANOVA is used to assess differences among groups. Significance was assessed with permutation tests in both cases. Variation among sampling groups (shallow MHI, shallow NWHI, O&#x02BB;ahu 30 m, 60 m, 90 m) was further examined and visualized using canonical analysis of principal coordinates (CAP) based on discriminant analysis [@andersonCanonicalAnalysisPrincipal2003] as implemented in the `CAPdiscrim` function in `BiodiversityR` [@kindtTreeDiversityAnalysis2005].

@@

Potential environmental drivers of shallow crab community structure were assembled from a previous study on environmental drivers of genetic diversity [@selkoeDNACoralReef2016], NOAA's National Coral Reef Monitoring Program (NCRMP), the Pacific Islands Ocean Observing System (PacIOOS), NASA Physical Oceanography Distributed Active Archive Center (PO.DAAC), and NASA Ocean Biology Distributed Active Archive Center (OB.DAAC) ([@tbl:env_table]). For details on how sea-surface temperature and chlorophyll data were compiled and aggregated, see Supplemental material. Due to logistical limitations, environmental data were collected only for shallow samples ($\le$ 30 m).

@@

Environmental variables were strongly clustered according to island group (MHI vs NWHI), with the separation primarily along the direction influenced by human impact, coral cover, sea-surface temperature, and chlorophyll ([@fig:fig_pca]). The best dbRDA model (`r permanova(db_modl,stat="F")`) explained `r pc(RsquareAdj(db_modl)$adj.r.squared,0.01)` (adjusted $\mathrm{R}^2$) of the variability in crab communities across the archipelago ([@fig:fig_dbrda]). `r str_to_sentence(english(nterm))` of the seven environmental variables tested were significant and sufficiently uncorrelated. The two drivers contributing most to explained variation were `r drivers$term[1]` (F = `r num(drivers$stat[1],0.01)`) and `r drivers$term[2]` (F = `r num(drivers$stat[2],0.01)`) ([@tbl:rda_table]). <!--TODO: perhaps include discussion of the vector lengths here as well, since chl-a is the shortest vector despite being the second most-significant factor.-->

@@

In the CAP analysis of island group and depth zone, ARMS units were correctly reassigned to groups `r pc(cap_depth$percent/100,0.1)` of the time. The first two axes explained `r pc(cap_var$x,0.1)` and `r pc(cap_var$y,0.1)` of the variation, respectively. Mesophotic samples (30--90 m) from O&#x02BB;ahu grouped separately from shallow samples collected across the entire ~2,500 km expanse of the archipelago ([@fig:fig_cap]). Additionally, variability among 30--90 m samples was visually equivalent to that among all shallow samples, although that was largely due to differences between 30 m and deeper sample groups ([@fig:fig_cap]).

@@

<br><br>

# Discussion {-}
Marine communities are structured by a suite of factors, but there remains no consensus for generalized mechanisms for coral reefs<!-- structuring communities in shallow coral reefs-->. Classic studies from the intertidal point to biotic factors determining lower limits and abiotic factors setting upper limits of vertical species distributions [@connellEffectsCompetitionPredation1961; @connellInfluenceInterspecificCompetition1961; @dennyPhysicalProcessesThat2001; @paineIntertidalCommunityStructure1974]. However, these conclusions describe distributions at individual sites and generalizations about the mechanisms and ecological processes that structure coral reef communities remain a subject of debate [@bellwoodEnvironmentalGeometricConstraints2005; @bellwoodSleepingFunctionalGroup2006; @carrBiodiversityPopulationRegulation2002; @connollyIndoPacificBiodiversityCoral2003; @dornelasCoralReefDiversity2006; @grahamImportanceStructuralComplexity2013; @komyakovaRelativeImportanceCoral2013]. In the Hawaiian archipelago, we found significant differences in the composition of cryptic crab communities between the populated high islands of the MHI and the uninhabited atolls of the NWHI. Moreover, these differences were driven by a combination of environmental (sea-surface temperature, chlorophyll concentration, depth), biotic (potential larval immigration), and anthropogenic (cumulative human impacts) factors. <!--Alpha diversity metrics show slight differences in the number of species and overall abundance of crabs in each sampled assemblage between the Main and Northwestern Hawaiian Islands, but CAP and PERMANOVA highlight significant differences in species assemblages between the regions. Differences in the species assemblages across regions are driven primarily by human impacts, cholorophyll a and sea surface temperature, although other factors such as larval connectivity, distance to nearest island, mean coral cover, and depth are also significant.-->

The Hawaiian Archipelago is among the most remote on the planet and encompasses a range of gradients (anthropogenic, biotic, abiotic), making it an ideal area to study the impacts of these factors on species assemblages across space. Human impacts are considerably higher in the populated MHI than in the protected and remote NWHI [@selkoeEvaluatingAnthropogenicThreats2008; @selkoeMapHumanImpacts2009; @selkoeDNACoralReef2016]. Although we did not consider individual effects here, an index representing cumulative anthropogenic impacts was the top driver of brachyuran community structure, similar to findings in previous work examining genetic diversity across the archipelago [@selkoeDNACoralReef2016]. The next-most significant driver, chlorophyll a, can be used as a proxy for primary productivity. Productivity gradients have been reported across the Hawaiian Archipelago, which coincide with differences in coral reef community composition [@selkoeDNACoralReef2016], endemic reef fish dominance [@friedlanderDominanceEndemicsReef2020], and survival rates of top predators [@bakerEffectVariableOceanic2007]. It is not surprising, therefore, that we find differences in the brachyuran crab communities are driven by these same factors across the Hawaiian archipelago.

@@

## Processing of satellite-derived environmental data
Level-3 mapped (9km) sea-surface temperature (SST) and chlorophyll A (chl-A) data were retrieved from NASA's Physical Oceanography Distributed Active Archive Center [PO.DAAC; @NASAJPL_2020] and Ocean Biology Distributed Active Archive Center [OB.DAAC; @NASAOceanBiologyProcessingGroup_2022] respectively. Monthly summary datasets were downloaded for the period of 2009--2016 and averaged over each of the ARMS unit soaking periods (e.g. 2009--2011, 2010--2012, etc.). Values (SST or chl-A) were extracted for the geographic coordinates of each sampling site from the averaged dataset for the relevant soaking period. Specific monthly-average dataset names can be found in @tbl:nasa_table.

@@

(p1 + p2) / (p3 + p4) & 
  plot_annotation(tag_levels = list(str_glue("({letters[1:4]})"))) & 
  theme(plot.tag = element_text(face="italic"))
cat("{#fig:fig_alpha}")
```

@@

(p1 + p2) & 
  plot_annotation(tag_levels = list(str_glue("({letters[1:2]})"))) & 
  theme(plot.tag = element_text(face="italic"))
cat("{#fig:fig_alpha2}")
```

@@

```{r nasa-table,results="asis",depenson="init"}
nasa_table <- read_csv(here("data","tables","nasa.csv"))
print_table(nasa_table,"nasa_table","NASA data repository filenames for CHL and SST satellite data",accuracy=1) 
```
